\documentclass[11pt]{article}
 
\usepackage[margin=0.8in]{geometry} 
\usepackage{amsmath,amsthm,amssymb}
\usepackage{relsize}
\usepackage{url}
\usepackage{comment}
\usepackage{graphicx}
\usepackage{booktabs}
 
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
 
\newenvironment{theorem}[2][Theorem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{lemma}[2][Lemma]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{exercise}[2][Exercise]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{problem}[2][Problem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{question}[2][Question]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{corollary}[2][Corollary]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{solution}[2][Solution]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
 
\begin{document}
 
% --------------------------------------------------------------
%                         Start here
% --------------------------------------------------------------
 
\title{Distribution Network Optimization - Stationery product case study }
\author{Utkarsh Konge\footnote{Contact:203190013@iitb.ac.in}}
\date{}
\maketitle

\section{Overview}
In my last communication, I briefly described the case of optimizing distribution network. Since then, I have made some progress. I had a brief talk with the winner of the challenge through which some things became more clear. 

Here, I am describing the problem in bit more detail. Then, I will add the analysis which can be done for the problem. This was a result of the brief discussion with the winner. I have modelled the system as MILP formulation which is presented here. This and other code is available in my Github repo. 

\section{Things to write}
\begin{itemize}
	\item In depth explanation of the problem statement
	\item Opportunities
	\item Approach - MILP
\end{itemize}

\section{Formulation}

\begin{table}
	\centering
	\begin{tabular}{cl}
		\toprule
		Variables & \\
		\midrule
		$x_{j,i}$ & Binary variable to denote if distributor $i$ is served from pooling location $j$\\
		$y_j$ & Binary variable to denote if pooling location $j$ needs to be used\\
		$g_{z,j}$ & Binary variable to denote if a zone $z$ is served from pooling location $j$\\
		$r_{z,j}$ & Total cost to deliver parcel from pooling location $j$ to zone $z$ \\
		$d_{j,i}$ & Demand of distributor $i$ served from pooling station $j$\\
		\bottomrule	
	\end{tabular}
	\caption{Parameters, Variables Table}
	\label{Tab:ParamSetVar}
\end{table}

%\bibliography{ref}
%\bibliographystyle{plainurl}


\end{document}